Continuous voting by approval and participation

### 2015-04-24 ApresentacoesArtigos/collectiveRanking/paper.tex
acertos minimos

\section{Discussion}
The above estimates are the best fit the researchers could deliver,
suitable for current needs and not found (yet) in literature.
The following questions should be addressed in near future:
\begin{itemize}
	\item Are there more adequate metrics for ranking proposals in the given setting?
    \item What are strong and weak aspects of the approach for collective recommendation?
    \item What thresholds will be the choice of community and will they be adjusted in time?
    \item Are there really no previous formalized model of this setting? If there is, what comparisons can we make on design, metrics and outcomes?
    \item To which extent will participation community and public managers legitimize this approach?
	\item What is the impact of this technological approach in public health care, social participation and the scientific community?
    \item To which extent society benefits from this continuous voting process? Is it worth the time spent by voters? How to evaluate this relation in terms of spent and gained resources?
\end{itemize}

Most importantly, this report is being delivered to the civil society and scientific community for consideration. Given the large number of possibilities for the collective ranking procedure, and the proliferation of solutions, research efforts might aim the organization of such procedures.

>>>>

\section{Discussion}
The above estimates are the best fit the researchers could deliver,
suitable for current needs and not found (yet) in literature.
The following questions should be addressed in near future:
\begin{itemize}
	\item Are there more adequate metrics for ranking proposals in the given setting?
    \item What are strong and weak aspects of the approach for collective recommendation?
    \item What thresholds will be the choice of community and will they be adjusted with time?
    \item Are there really no previous formalized model of this setting? If there is, what comparisons can we make on design, metrics and outcomes?
    \item To which extent will participation community and public managers legitimize this approach?
	\item What is the impact of this technological approach in public health care, social participation and the scientific community?
    \item To which extent society benefits from this continuous voting process? Is it worth the time spent by voters? How to evaluate this relation in terms of spent and gained resources?
\end{itemize}

Most importantly, this report is being delivered to the civil society and the scientific community for consideration. Given the large number of possibilities for the collective ranking procedure, and the proliferation of solutions, research efforts might aim the organization of such procedures.
